KidsAIR: exposure model

### 2020-05-05 exposure_covariate_associations.Rmd
missing data summary updates

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo" & area == "WMT") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  left_join(sums_temp_change, by = c("area", "home")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home")) %>% 
  mutate(home_act_door_2level = cut(home_act_door, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))

@@

@@

d23 <- analysis_function("burn_level_3level", "Burn level")
d24 <- analysis_function("wood_collect_2level", "Wood collect time")
d25 <- analysis_function("wood_collect_method_2level", "Wood collect method")
d26 <- analysis_function("wood_cords", "Wood cords")

>>>>

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  left_join(sums_temp_change, by = c("area", "home")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home")) %>% 
  mutate(home_act_door_2level = cut(home_act_door, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))

@@

analysis_function <- function(covar, label, 
                              dataset = analysis_data){

  analysis_data <- dataset %>% 
    filter(winter_id == 1 & treatment == "Placebo") %>% 
    rename(analysis_covar = covar)

  table(analysis_data$analysis_covar)

@@

d23 <- analysis_function("burn_level_3level", "Burn level")
d24 <- analysis_function("wood_collect_2level", "Wood collect time")
d25 <- analysis_function("wood_collect_method_2level", "Wood collect method")
d26 <- analysis_function("wood_cords", "Wood cords")
data_check <- analysis_data %>% 
  filter(area == "NN")
table(data_check$education_3level)
table(!is.na(data_check$mean_temp_sampling_period_5))

### 2020-05-05 exposure_models.Rmd
missing data summary updates

# Summary Statistics
missing_summary <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(residents_smoke), "missing yes", "missing no")) %>%
  group_by(area, missing_var) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc_miss = n/total_n*100) %>% 
  select(area, missing_var, n, perc_miss, mean_pm, sd_pm, median_pm)
missing_summary

# T-tests
missing_test <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(residents_smoke), "missing yes", "missing no")) %>% 
  filter(!is.na(log_pm_mean_sampling_period) & !is.na(missing_var))

@@

missing_summary <- complete_case %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_pm, sd_pm, median_pm)
missing_summary

@@

missing_summary <- missing_data %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_pm, sd_pm, median_pm)
missing_summary

>>>>

# Summary Statistics
missing_summary <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(stove_grade_3level), "missing yes", "missing no")) %>%
  group_by(area, missing_var) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc_miss = n/total_n*100) %>% 
  select(area, missing_var, n, perc_miss, mean_pm, sd_pm, median_pm)
missing_summary

# T-tests
missing_test <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(home_act_door_2level), "missing yes", "missing no")) %>% 
  filter(!is.na(log_pm_mean_sampling_period) & !is.na(missing_var))

@@

missing_summary <- complete_case %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_pm = mean(mean_temp_sampling_period_5, na.rm = TRUE), 
            sd_pm = sd(mean_temp_sampling_period_5, na.rm = TRUE),
            median_pm = median(mean_temp_sampling_period_5, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_pm, sd_pm, median_pm)
missing_summary

@@

missing_summary <- missing_data %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_pm = mean(mean_temp_sampling_period_5, na.rm = TRUE), 
            sd_pm = sd(mean_temp_sampling_period_5, na.rm = TRUE),
            median_pm = median(mean_temp_sampling_period_5, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_pm, sd_pm, median_pm)
missing_summary
